What We Eval in the Shadows

### 2021-04-13 analysis/environments.Rmd
Number of categories per site

#TODO: create tags for the poly categories df

And what if we classify by using the most present category for site?
```{r}
majority_category <- env_categories %>% group_by(src_ref, category) %>% summarise(n_calls = sum(duplicates)) %>%
  summarize(category = first(category, order_by = order(n_calls, decreasing = TRUE)), n = n(), prop_first = max(n_calls) / sum(n_calls))

majority_category %>% group_by(category) %>% summarise(n = n_distinct(src_ref)) %>% arrange(desc(n)) %>% mutate(pc = ratio(n, nb_call_sites), cpc = cumsum(pc))
```

>>>>

nrows <- 4
r_vec("nb category envir", nrows, poly_categories$n_categories)
r_vec("nb category envir sites", nrows, poly_categories$n)
r_vec("nb category envir percent", nrows, poly_categories$pc)
r_vec("nb category envir cumsum percent", nrows, poly_categories$cpc)
```

And what if we classify by using the most present category for site?
```{r}
majority_category <- env_categories %>% group_by(src_ref, category) %>% summarise(n_calls = sum(duplicates)) %>%
  summarize(categories = paste(sort(unique(category)), collapse = " ; "), category = first(category, order_by = order(n_calls, decreasing = TRUE)), n = n(), prop_first = max(n_calls) / sum(n_calls), )

majority_category %>% group_by(category) %>% summarise(n = n_distinct(src_ref)) %>% arrange(desc(n)) %>% mutate(pc = ratio(n, nb_call_sites), cpc = cumsum(pc))

majority_category %>% group_by(categories) %>% summarise(n = n_distinct(src_ref)) %>% arrange(desc(n)) %>% mutate(pc = ratio(n, nb_call_sites), cpc = cumsum(pc))
```

### 2021-04-13 paper/main.tex
Number of categories per site

\begin{table}[h]
\centering
\small
\begin{minipage}{4cm}
  \begin{tabular}{r|r|r}\hline
 Environment & \#sites & \%sites \\\hline
 Function & \packageNbFunctionEnvSites &  \packageNbFunctionEnvSitePercent\\
 Synthetic & \packageNbSyntheticEnvSites & \packageNbSyntheticEnvSitePercent \\
 Global &  \packageNbStrictGlobalEnvSites & \packageNbStrictGlobalEnvSitePercent \\
 Package & \packageNbPackageNamespaceEnvSites & \packageNbPackageNamespaceEnvSitePercent \\\hline
\end{tabular}
\caption{Environments per site} \label{tab:highlevelenvironments}
\end{minipage} \hspace{1cm}
\begin{minipage}{3.7cm}\centering
\begin{tabular}{r|r|r}\hline
 Offset & \#sites & \%sites \\\hline
  \packageCallerEnvHierarchyNamea & \packageCallerEnvHierarchySitesaRnd & \packageCallerEnvHierarchySitePercenta \\
  \packageCallerEnvHierarchyNameb& \packageCallerEnvHierarchySitesbRnd & \packageCallerEnvHierarchySitePercentb \\
  \packageCallerEnvHierarchyNamec& \packageCallerEnvHierarchySitescRnd & \packageCallerEnvHierarchySitePercentc  \\
  > 3& \packageNbFarAwayCallerSites &  \packageNbFarAwayCallerSitePercent \\\hline
 \end{tabular}
\caption{Function offset}\label{tab:funoffset}
\end{minipage}\hspace{1cm}
\begin{minipage}{3.8cm}
\begin{tabular}{r|r|r} \hline
Parent & \#sites & \%sites \\\hline
Function & \packageNewEnvCategorySitesa & \packageNewEnvCategorySitePercenta \\
Package & \packageNewEnvCategorySitesb &  \packageNewEnvCategorySitePercentb\\
Global & \packageNewEnvCategorySitesc & \packageNewEnvCategorySitePercentc \\
Empty & \packageNewEnvCategorySitesd & \packageNewEnvCategorySitePercentd \\\hline
\end{tabular} \label{tab:newenvs}
\caption{Wrapper envs.}
\end{minipage}

\vspace{-0.3cm} \begin{minipage}{\textwidth} \footnotesize
One site could appear in several categories. However, most sites, \ie \packageNbOneCategoryEnvirSitePercent, have only kind of the above environments passed to them.
\end{minipage}
\end{table}

>>>>

One site could appear in several categories. However, most sites, \ie \packageNbOneCategoryEnvirSitePercent, have only kind of the above environments passed to them, as shown in Table~\ref{tab:polyenvir}.

\begin{table}[h]
\centering
\small
\begin{minipage}{4cm}
  \begin{tabular}{r|r|r}\hline
 Environment & \#sites & \%sites \\\hline
 Function & \packageNbFunctionEnvSites &  \packageNbFunctionEnvSitePercent\\
 Synthetic & \packageNbSyntheticEnvSites & \packageNbSyntheticEnvSitePercent \\
 Global &  \packageNbStrictGlobalEnvSites & \packageNbStrictGlobalEnvSitePercent \\
 Package & \packageNbPackageNamespaceEnvSites & \packageNbPackageNamespaceEnvSitePercent \\\hline
\end{tabular}
\caption{Environments per site} \label{tab:highlevelenvironments}
\end{minipage} \hspace{1cm}
\begin{minipage}{3.7cm}\centering
\begin{tabular}{r|r|r}\hline
 Offset & \#sites & \%sites \\\hline
  \packageCallerEnvHierarchyNamea & \packageCallerEnvHierarchySitesaRnd & \packageCallerEnvHierarchySitePercenta \\
  \packageCallerEnvHierarchyNameb& \packageCallerEnvHierarchySitesbRnd & \packageCallerEnvHierarchySitePercentb \\
  \packageCallerEnvHierarchyNamec& \packageCallerEnvHierarchySitescRnd & \packageCallerEnvHierarchySitePercentc  \\
  > 3& \packageNbFarAwayCallerSites &  \packageNbFarAwayCallerSitePercent \\\hline
 \end{tabular}
\caption{Function offset}\label{tab:funoffset}
\end{minipage}\hspace{1cm}
\begin{minipage}{3.8cm}
\begin{tabular}{r|r|r} \hline
Parent & \#sites & \%sites \\\hline
Function & \packageNewEnvCategorySitesa & \packageNewEnvCategorySitePercenta \\
Package & \packageNewEnvCategorySitesb &  \packageNewEnvCategorySitePercentb\\
Global & \packageNewEnvCategorySitesc & \packageNewEnvCategorySitePercentc \\
Empty & \packageNewEnvCategorySitesd & \packageNewEnvCategorySitePercentd \\\hline
\end{tabular} \label{tab:newenvs}
\caption{Wrapper envs.}
\end{minipage}
\begin{minipage}{\textwidth} 
   \centering
   \begin{tabular}{c|c|c}
       \hline
       \#categories & \#sites &  \%sites \\ \hline
       \packageNbCategoryEnvira & \packageNbCategoryEnvirSitesaRnd &  \packageNbCategoryEnvirPercenta\\
       \packageNbCategoryEnvirb &  \packageNbCategoryEnvirSitesbRnd & \packageNbCategoryEnvirPercentb \\
       \packageNbCategoryEnvirc & \packageNbCategoryEnvirSitescRnd &  \packageNbCategoryEnvirPercentc\\
       \packageNbCategoryEnvird & \packageNbCategoryEnvirSitesdRnd & \packageNbCategoryEnvirPercentd\\
       \hline
   \end{tabular} \label{tab:polyenvir}
   \caption{Number of categories per site.}
\end{minipage}
\end{table}
